Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-17 files/Chapter4/Validity_Timo.tex
chapter 4
Chapter 4

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}

@@

The article \cite{LVV09} is titled `Comparison of linear beam theories'. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. The authors start by presenting the models. These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1. The authors also look at the existence and uniqueness of the models, which is covered in Chapter 2 of this dissertation. The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.

@@

As mentioned in the introduction, the height of the two beams can be set to be the same by considering the parameter $\alpha$ for the Timoshenko beam model and the parameter $h$ for the two-dimensional beam model.

@@

\subsection{Comparing the mode shapes}
Recall from the introduction, that the investigation is focussed on beam-type problems. The two-dimensional model is for an elastic body, and not specific to a beam, like the Timoshenko beam model. Therefore there are non-beam type behaviour that can be expected from the two-dimensional model. This is also be reflected in the eigenvalues of the two-dimensional model.

Therefore a method is required to compare and match the eigenvalues of the two models. In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues. Recall \textcolor{red}{****} that eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam type eigenvalues. The other eigenvalues are called non-beam type eigenvalues. This naming convention is used by the authors of \cite{LVV09}.

@@

\subsubsection{Shape of the cross-sections}
The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear. For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam. The cross-sections however remain a straight line.\\

For the two-dimensional beam, the shape of the cross-section can deform into a s-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here. This is a difference between the two models that are inherent to their definitions.\\

@@

Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam. The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.

@@

These figures are examples that show how similar the mode shapes of the two models are. This specific example is for $\alpha = 4800$, which represents a long, narrow beam. The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and fat beam.

\subsubsection{Remark:} Note that the overall shape is more important than the actual fit. This is because any multiple of a eigenvector is still an eigenvector. The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.

\subsection{Comparing the eigenvalues}
Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared.

@@

\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
		\hline
		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
		2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
	\end{tabular}\label{Results_LVV09}
\end{table}

@@

This table shows that the eigenvalues compare very well. The non-beam type eigenvalues are highlighted in grey. For a short fat beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$. This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam. But overall the Timoshenko beam compares very well.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
            title={Relative Error of Eigenvalues for Different Values of Alpha},
            xlabel={Eigenvalue},
            ylabel={Relative Error (\%)},
            legend pos=north east,
            grid=major,
        ]
        % Alpha = 300
        \addplot coordinates {
            (1,0.4875) (2,1.1106) (3,0) (4,1.7895) (5,2.4560) (6,0) (7,2.9630) (8,1.4324) (9,0) (10,2.9530)
            (11,0.5735) (12,0) (13,0.8375) (14,0.5643) (15,0) (16,0.4757) (17,0) (18,1.1240) (19,0) (20,1.9740)
        };
        \addlegendentry{\(\alpha = 300\)}

        % Alpha = 1200
        \addplot coordinates {
            (1,0.2337) (2,0.4217) (3,0) (4,0.7198) (5,1.0738) (6,1.4507) (7,0) (8,1.6244) (9,2.1618) (10,0)
            (11,2.4560) (12,0) (13,2.7265) (14,0) (15,0) (16,5.2392) (17,0) (18,3.2823) (19,3.0864) (20,0)
        };
        \addlegendentry{\(\alpha = 1200\)}

        % Alpha = 4800
        \addplot coordinates {
            (1,0.1125) (2,0.1661) (3,0.2574) (4,0) (5,0.3824) (6,0.5373) (7,0.7065) (8,0) (9,0.9950) (10,1.0740)
            (11,0) (12,1.2680) (13,1.4507) (14,0) (15,0) (16,1.8120) (17,0) (18,1.9850) (19,2.1618) (20,0)
        };
        \addlegendentry{\(\alpha = 4800\)}

        % Alpha = 10800
        \addplot coordinates {
            (1,0.0841) (2,0.1009) (3,0.1287) (4,0.2052) (5,0.3824) (6,0.2817) (7,0.3725) (8,0.4712) (9,0) (10,0.5940)
            (11,0.7005) (12,0.8140) (13,0.9307) (14,0) (15,0) (16,1.8120) (17,1.2150) (18,1.9850) (19,2.1618) (20,2.8860)
        };
        \addlegendentry{\(\alpha = 10800\)}

        \end{axis}
    \end{tikzpicture}
    \caption{Plot of the relative error for each eigenvalue and each value of \(\alpha\).}
    \label{fig:relative_error_plot}
\end{figure}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the model for a cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}

@@

The article \cite{LVV09} is titled `Comparison of linear beam theories'. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. The authors start by presenting the models. These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1. The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation. The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.

@@

In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
introduced. The paramater is given here again for convenience,
\begin{eqnarray*}
	\alpha = \frac{A\ell^2}{I}.
\end{eqnarray*}

The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$. Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$. The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.

Substituting these values into the equation for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$,
\begin{eqnarray}
	\alpha & = & \frac{12}{h^2}, \label{eq:alpha-h-relationship}
\end{eqnarray}
or equivalently,
\begin{eqnarray}
	h & = & \sqrt{\frac{12}{\alpha}}. \label{eq:h-alpha-relationship}
\end{eqnarray}

These equations \eqref{eq:alpha-h-relationship} or \eqref{eq:h-alpha-relationship} describe the relationship between the height of the beam and the parameter $\alpha$. Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.

@@

\subsection{Comparing the mode shapes}
Recall from the introduction, that the investigation is focussed on beam-type problems. The two-dimensional model is for an eigenvalue problem and and not specific to beam-type applications, like the Timoshenko beam model. Therefore there are non-beam type modes that can be expected from the two-dimensional model. This is also be reflected in the eigenvalues of the two-dimensional model and therefore eigenvalues irrelevant to beam-type problems exits.

Therefore a method is required to compare and match the eigenvalues of the two models. In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues. Eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam-type eigenvalues. The other eigenvalues are called non-beam type eigenvalues by the authors.

@@

\subsubsection{Shape of the cross-sections}
The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear. For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam. The cross-sections however remain a straight line.

For the two-dimensional beam, the shape of the cross-section can deform into a S-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.

@@

Similarly, figure \ref{fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam. The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.

@@

These figures are examples that show how similar the mode shapes of the two models are. This specific example is for $\alpha = 4800$, which represents a typical beam. The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and thick beam.

\subsubsection{Remark:} Note that the overall shape is important. This is because any multiple of a eigenvector is still an eigenvector. The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.

\subsection{Comparing the eigenvalues}
Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared. In the tables, Timo refers to the Timoshenko beam and 2D refers to the two-dimensional beam.

@@

\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
	\begin{tabular}{|c|c|c||c|c|c|}
		\hline
		\multicolumn{3}{|c||}{Results from [LVV09]} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & ~ & 2D & Timo  \\ \hline
		1 & 0.0317 & 0.0316 & 1 & 0.031713 & 0.031639  \\ 
		2 & 1.14 & 1.14  & 2 & 1.1413 & 1.1365  \\ 
		3 & 7.72 & - & 3 & 7.7161 & - \\ 
		4 & 7.92 & 7.86 &  4 & 7.918 & 7.8617    \\ 
		5 & 26.2 & 25.9 & 5 & 26.148 & 25.869   \\ 
		6 & 60.8 & 59.9 & 6 & 60.816 & 59.946  \\ 
		7 & 69.3 & - & 7 & 69.344 & -  \\ 
		8 & 115 & 113 &  8 & 115.28 & 113.23   \\ 
		9 & 192 & 188 &  9 & 191.57 & 187.55   \\ 
		10 & 192 & - & 10 & 192.03 & -  \\ 
		11 & 291 & 284 & 11 & 290.76 & 283.81   \\ \hline
	\end{tabular}\label{Results_LVV09}
\end{table}

\begin{comment}
\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
		\hline
		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
		2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
	\end{tabular}\label{Results_LVV09}
\end{table}
\end{comment}

@@

This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well. The non-beam type eigenvalues are highlighted in grey. For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$. This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam. But overall the Timoshenko beam compares very well.

@@

### 2023-11-17 files/Chapter6/Validity_Timo.tex
Chapter 6
Chapter 4

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}

@@

Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.

@@

					\end{tikzpicture}
				\end{center}
				\subcaption{Two-Dimensional Cantilever Beam}
			\end{minipage}
		}
	}
\end{figure}\label{fig:compare:1D+2D}

@@

\begin{figure}[H]
    \centering
    \begin{adjustbox}{center}
        \includegraphics[scale=0.7]{Convergence.png}
    \end{adjustbox}
    \caption{Rate of convergence of the first 20 eigenvalues.}
    \label{fig:conv_2d_eig}
\end{figure}

Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.

@@

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam1.jpg}
				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam2.png}
				\subcaption{Timoshenko - $\lambda_5 = 21.794$}
				\label{fig:minipage1}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam2.jpg}
				\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam1.png}
				\subcaption{Timoshenko - $\lambda_6 = 45.390$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
		}
	}
\end{figure}
\FloatBarrier

\subsubsection{Shapes relating to non-beam type eigenvalues}
The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam1.jpg}
				\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam2.jpg}
				\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
		}
	}
\end{figure}
\FloatBarrier

@@

\end{tikzpicture}
	\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
\end{figure}
\FloatBarrier

Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section. The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam. This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam given by $\phi$.

\subsubsection{Direct comparison of mode shapes}
Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam. For the two-dimensional model, the center line of the displacement of the beam is shown. For the Timoshenko beam, the displacement $w$ is shown.

\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2D.png}
			\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:w}}}
\end{figure}
\FloatBarrier

Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam. The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.

\FloatBarrier
\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2Dphi.png}
			\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:phi}}}
\end{figure}
\FloatBarrier

@@

\subsubsection{Remark:} Note that the overall shape is more important than the actual fit. This is because any multiple of a eigenvector is still an eigenvector. The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.

@@

\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
		\hline
		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
		2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
	\end{tabular}\label{Results_LVV09}
\end{table}

@@

	\label{tab:Timo}%

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam_chapter6}

@@

Figure \ref{fig:compare:1D+2D_chapter6} shows the two beams side-by-side.

@@

					\end{tikzpicture}
				\end{center}
				\subcaption{Two-Dimensional Cantilever Beam}
			\end{minipage}
		}
	}
\end{figure}\label{fig:compare:1D+2D_chapter6}

@@

\begin{figure}[H]
    \centering
    \begin{adjustbox}{center}
        \includegraphics[scale=0.7]{Convergence.png}
    \end{adjustbox}
    \caption{Rate of convergence of the first 20 eigenvalues.}
    \label{fig:conv_2d_eig_chapter6}
\end{figure}

Figure \ref{fig:conv_2d_eig_chapter6} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.

@@

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam1.jpg}
				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
				\label{fig:minipage2_chapter6}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam2.png}
				\subcaption{Timoshenko - $\lambda_5 = 21.794$}
				\label{fig:minipage1_chapter6}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam2.jpg}
				\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
				\label{fig:minipage2_chapter6}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam1.png}
				\subcaption{Timoshenko - $\lambda_6 = 45.390$}
				\label{fig:minipage1_chapter6}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
		}
	}
\end{figure}
\FloatBarrier

\subsubsection{Shapes relating to non-beam type eigenvalues}
The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam1.jpg}
				\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
				\label{fig:minipage2_chapter6}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam2.jpg}
				\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
				\label{fig:minipage1_chapter6}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
		}
	}
\end{figure}
\FloatBarrier

@@

\end{tikzpicture}
	\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s_chapter6}
\end{figure}
\FloatBarrier

Note that figure \ref{fig:s_chapter6} shows an exaggerated example of the deformation of a cross-section. The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam. This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam given by $\phi$.

\subsubsection{Direct comparison of mode shapes}
Figure \ref{fig:w_chapter6} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam. For the two-dimensional model, the center line of the displacement of the beam is shown. For the Timoshenko beam, the displacement $w$ is shown.

\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2D.png}
			\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:w_chapter6}}}
\end{figure}
\FloatBarrier

Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam. The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s_chapter6}.

\FloatBarrier
\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2Dphi.png}
			\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:phi_chapter6}}}
\end{figure}
\FloatBarrier

@@

\subsubsection{Remark:} Note that the overall shape is more important than the actual fit. This is because any multiple of a eigenvector is still an eigenvector. The mode shapes were specifically scaled to obtain figures \ref{fig:w_chapter6} and \ref{fig:phi_chapter6}.

@@

\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
		\hline
		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
		2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
	\end{tabular}\label{Results_LVV09_chapter6}
\end{table}

@@

	\label{tab:Timo_chapter6}%
